---
title: "Homework 1"
author: "Justin Li"
date: "2022-09-24"
output: github_document
---

```{r setup, include=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```


1. How many flights have a missing dep_time? What other variables are missing? 
What might these rows represent?
```{r}
flights %>%
  filter(is.na(dep_time))
```

There are 8255 flights that have a missing dep_time. Other variables that are
missing are dep_delay, arr_time, arr_delay, and air_time. These rows suggest
that these rows were canceled.

2. Currently dep_time and sched_dep_time are convenient to look at, but hard to 
compute with because they’re not really continuous numbers. Convert them to a 
more convenient representation of number of minutes since midnight.

```{r}
flights %>%
  mutate(new_dep_time = ((dep_time %/% 100) * 60) + dep_time %% 100,
   new_sched_dep_time = ((sched_dep_time %/% 100) * 60) + sched_dep_time %% 100)
```

3. Look at the number of canceled flights per day. Is there a pattern? Is the 
proportion of canceled flights related to the average delay? Use multiple dyplr 
operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point().
```{r}
flights %>%
  group_by(day) %>%
  summarise(avg_delay = mean(dep_delay, na.rm = T),
            total_flights = n(),
            canceled_flights = sum(is.na(dep_delay)),
            prop_canceled_flights = canceled_flights / total_flights) %>%
  ggplot(aes(x = avg_delay, y = prop_canceled_flights)) + geom_point()
```

It seems like as average delay increases, so does the proportion of canceled
flights.
